\documentclass[10pt]{article}
\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{ragged2e}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{geometry}

\geometry{left=0.75in,right=0.75in,top=0.6in,bottom=0.6in}
\setlength{\parindent}{0pt}
\RaggedRight

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\\begin{document}

{\LARGE \\textbf{MANGESH SURESH BIDE}} \\
Rmangeshsbide@gmail.com $\cdot$ \\href{https://www.linkedin.com/in/mangesh\textendash{} bide/}{linkedin.com/in/mangesh\textendash{} bide/} $\cdot$ \\href{https://github.com/1mangesh1}{github.com/1mangesh1} \\section*{\Large Education}
\\textbf{B. Tech in Computer Engineering} \hfill 2021	\textendash{} 2024 \\
R. C. Patel Institute of Technology, Shirpur, Maharashtra \\
CGPA: 7.98/10 \\vspace{1pt}
\\textbf{Diploma in Computer Engineering} \hfill 2019	\textendash{} 2021 \\
R. C. Patel Polytechnic, Shirpur, Maharashtra \\
Percentage: 93.89\% \\section*{\Large Skills}
\\textbf{Programming Languages:} Python, JavaScript (ES6+), TypeScript, Java, PHP \\textbf{Backend Frameworks:} Django (REST Framework, ViewSets), NestJS, Node.js (Express), Laravel \\textbf{Frontend Technologies:} React.js, Next.js, Tailwind CSS, shadcn/ui, HTML5, CSS3 \\textbf{DevOps \& Tooling:} Docker, GitHub Actions, Terraform, Git, GitLab, Shell Scripting \\textbf{Cloud Platforms \& Deployment:} AWS (EC2, S3, IAM, Cognito), Firebase, Vercel, CI/CD Pipelines \\textbf{Database Systems:} PostgreSQL, MySQL, MongoDB, DynamoDB \\textbf{Machine Learning \& AI:} TensorFlow, PyTorch, Eden AI APIs, Computer Vision \\textbf{Project Tools:} Jira, Notion, Slack, Figma (basic) \\textbf{Soft Skills:} Clear Communication, Team Collaboration, Problem\textendash{} Solving, Ownership, Rapid Learning \\section*{\Large Experience}
\\textbf{Software Development Engineer\textendash{} I} \hfill Feb 2025	\textendash{} Present \\
Houseworks Technologies 	\textendash{} Remote \\begin{itemize}\\setlist[itemize]{leftmargin=15pt, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=2pt}
    \\item Led backend development for a critical healthcare product using Django, PostgreSQL, and AWS, managing core modules like user authentication, ICD (International Classification of Diseases) coding, and appointment workflows. \\item Designed and implemented scalable infrastructure with Terraform and Docker, enabling one\textendash{} click deployment for staging and production environments. \\item Streamlined CI/CD (Continuous Integration/Continuous Deployment) processes using GitHub Actions and Shell scripting, reducing deployment time by 70\% and eliminating manual overhead. \\item Added hot\textendash{} reload support and environment\textendash{} aware Docker setups to accelerate development feedback loops. \\item Contributed to front\textendash{} end features using React.js, Next.js, and shadcn/ui, ensuring seamless user experience and performance. \\item Collaborated across cross\textendash{} functional teams using Jira, Notion, and Slack; actively participated in architecture discussions and product grooming sessions. \\item Practiced clean code principles (SOLID, DRY), wrote unit tests with meaningful assertions, and consistently delivered well\textendash{} documented, production\textendash{} ready code. \\end{itemize}
\\vspace{1pt}
\\textbf{Software Development Engineer Intern} \hfill Feb 2025	\textendash{} Mar 2025 \\
Houseworks Technologies 	\textendash{} Remote \\begin{itemize}\\setlist[itemize]{leftmargin=15pt, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=2pt}
    \\item Automated infrastructure setup for staging environments using Terraform Workspaces and EC2 (Elastic Compute Cloud) provisioning. \\item Optimized CI/CD pipelines and added hot\textendash{} reloading for Django with Docker Compose and Gunicorn. \\item Contributed to internal product UI with React.js, Next.js, and shadcn/ui, maintaining design consistency and accessibility. \\end{itemize}
\\vspace{1pt}
\\textbf{Software Development Engineer Trainee} \hfill Oct 2024	\textendash{} Feb 2025 \\
Procedure Technologies, Mumbai, Maharashtra \\begin{itemize}\\setlist[itemize]{leftmargin=15pt, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=2pt}
    \\item Gained hands\textendash{} on experience in full\textendash{} stack development with React.js, Next.js, TypeScript, and NestJS. \\item Containerized apps using Docker and managed infrastructure with Terraform, following software design patterns and best practices. \\item Learned system design principles and applied clean code practices in live projects. \\end{itemize}
\\vspace{1pt}
\\textbf{Backend Developer Intern} \hfill Feb 2024	\textendash{} July 2024 \\
Netwin Infosolutions Pvt Ltd, Nashik, Maharashtra \\begin{itemize}\\setlist[itemize]{leftmargin=15pt, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=2pt}
    \\item Developed RESTful APIs and integrated JWT (JSON Web Token) authentication for a Flutter\textendash{} based activity tracker live project using Django and MySQL. \\item Implemented image\textendash{} based search functionality for an eCommerce app by integrating a machine learning API from Eden AI. \\item Created an admin panel for managing users, roles, tickets, and activities. \\item Set up email\textendash{} based password reset and OTP (One\textendash{} Time Password)-based activity verification using Twilio. \\end{itemize}
\\vspace{1pt}
\\textbf{President} \hfill Feb 2023	\textendash{} April 2024 \\
Akatsuki Coding Club, R.C. Patel Institute of Technology, Shirpur \\begin{itemize}\\setlist[itemize]{leftmargin=15pt, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=2pt}
    \\item Led the club’s activities, including organizing coding competitions and technical workshops for over 100 students. \\end{itemize}

\\section*{\Large Projects}
\\textbf{Expense Tracking and Budgeting API} (NestJS, TypeORM, Swagger, JWT) \\begin{itemize}\\setlist[itemize]{leftmargin=15pt, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=2pt}
    \\item Designed a modular API for managing expenses with JWT\textendash{} based authentication, role\textendash{} based access control, data aggregation, and scheduled summaries. \\item Integrated Swagger for live API documentation and tested endpoints using Postman and Jest. \\end{itemize}
\\vspace{1pt}
\\textbf{Infrastructure\textendash{} as\textendash{} Code Deployment for ChatApp} (Terraform, AWS EC2, DNS) \\begin{itemize}\\setlist[itemize]{leftmargin=15pt, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=2pt}
    \\item Provisioned and deployed a real\textendash{} time chat application using Terraform scripts on AWS EC2, ensuring scalability and high availability. \\item Configured DNS routing and SSH for CI/CD with minimal manual intervention. \\end{itemize}
\\vspace{1pt}
\\textbf{CrimiFace \t\textendash{} Criminal Recognition System} (Python, TensorFlow) \\begin{itemize}\\setlist[itemize]{leftmargin=15pt, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=2pt}
    \\item Built a facial recognition tool using ML models to detect and match faces against a criminal database. \\item Applied OpenCV and TensorFlow for image preprocessing, model training, and real\textendash{} time inference. \\end{itemize}
\\vspace{1pt}
\\textbf{Real\textendash{} time ChatApp} (Node.js, Express, Socket.io) \\begin{itemize}\\setlist[itemize]{leftmargin=15pt, topsep=0pt, parsep=0pt, partopsep=0pt, itemsep=2pt}
    \\item Developed a chat platform with private messaging, room\textendash{} based communication, and activity logging using WebSockets. \\item Ensured fault\textendash{} tolerance and event\textendash{} based communication for seamless real\textendash{} time interaction. \\end{itemize}

\\end{document}
